---
title: "Agent-based models of collaborative problem solving"
author: "Pierce Edmiston"
output:
  html_document:
    theme: flatly
    toc: true
    toc_depth: 1
---
```{r peaks-config, include=FALSE}
library(knitr)
library(crotchet)

fig_width <- 6
fig_height <- 4

opts_chunk$set(
  echo = FALSE,
  message = FALSE,
  warning = FALSE,
  results = "hide",
  fig.width = fig_width,
  fig.height = fig_height,
  cache = TRUE
)

chunks_dir <- "R"
read_chunk(file.path(chunks_dir, "peaks.R"))
```
```{r peaks-setup}
```

# Introduction {-}

Humans have the unique ability to use and improve cultural products
that were invented by someone else. We do this regularly and more effectively
than any other species of animal. This ability is beneficial in that it allows
cultures to accumulate improvements to tools and other solutions to problems.
The result of this accumulation is that individuals are able to use cultural
products that are so complex as to be impossible for any individual to invent
on their own.

In looking for evidence of cumulative cultural evolution in non-human species,
a key requirement is that the tools or other cultural products sustained in
a community could not have been invented by individuals working alone. However,
what are the conditions under which generations of problem solvers working one
after the other can arrive at solutions that could not be reached by
individuals working alone or in parallel? Under what conditions does
inheritance in problem solving provide an advantage over alternative ways of
allocating the same number of labor hours? In this research, I use
computational models to explore the conditions under which inheritance results
in generations of problem solvers achieving problem solutions that were
unlikely to be obtained by individuals working alone, even for the same total
amount of time.

(ref:peaks-team-structures) Simulated problem solving strategies. All strategies
are given the same number of total guesses to find the peak in the solution landscape.
Diachronic problem solvers inherit from the previous generation. Synchronic problem
solvers combine their skills for a larger search area on each trial. Isolated
individuals work alone.

```{r peaks-team-structures, fig.width=2, fig.cap='(ref:peaks-team-structures)'}
draw_graphviz("team-structures", package = "totems")
```

# Methods {-}

```{r peaks-methods}
```

## Landscapes {-}

(ref:simple-hill) A simple solution landscape. Agents varied in vision in either
x or y dimension. On each trial agents sampled a random position within their
visual range, and if it was higher on the landscape than they were currently, they
moved there.

```{r simple-hill, fig.cap='(ref:simple-hill)'}
limits <- seq(-100, 100, by = 10)
z <- expand.grid(x = limits, y = limits) %>%
     mutate(z = -x^2 - y^2)
lattice::wireframe(z ~ x * y, data = z)
```

## Ability as vision {-}

(ref:ability-as-vision) Ability as vision. Teams of two agents could allocate
the same total skill in different ways. Identical teams shared the same abilities
in both dimensions. Complementary teams had "equal but opposite" skills.

```{r ability-as-vision, fig.width=6, fig.height=6, fig.cap='(ref:ability-as-vision)'}
grid.arrange(
  arrangeGrob(gg_single_dimension, gg_two_dimensions, nrow = 1),
  gg_differing_skills,
  ncol = 1
)
```

## Vision and search areas {-}

(ref:search-areas) Search areas for individual agents.

```{r search-areas, fig.width=8, fig.height=2, fig.cap='(ref:search-areas)'}
gg_search_rects
```

(ref:search-areas-by-strategy) Search areas for teams of agents.

```{r search-areas-by-strategy, fig.cap='(ref:search-areas-by-strategy)'}
gg_search_areas_by_strategy
```

# Experiments {-}

```{r peaks-experiments}
```

## Identical teammates {-}

```{r identical-teammates, fig.keep="last"}
grid.arrange(gg_identical_team_timeline,
             gg_identical_team_final_fitness, nrow = 1)
```

```{r random-walk-plot}
random_walk_plot
```

## Differing skills {-}

```{r differing-skills, fig.width=10, fig.keep="last"}
grid.arrange(gg_differing_skills_timeline,
             gg_differing_skills_final_fitness,
             nrow = 1)
```

```{r differing-skills-walk, fig.width = 8, fig.height = 5}
gg_differing_skills_walk
```

## Solo teams {-}

```{r solo-teams, fig.keep="last", fig.width=10}
grid.arrange(gg_solo_teams_timeline, gg_solo_teams_final_fitness, nrow = 1)
```

## Number of exchanges {-}

```{r number-of-exchanges}
```

## Aggregate functions {-}

```{r aggregate-functions}
gg_aggregate
```

## Variable feedback {-}

```{r variable-feedback, fig.width = fig_width * 2}
grid.arrange(feedback_trials_plot, variable_feedback_plot, nrow = 1)
```

# Discussion
